---
author: "Church Army's Research Team"
format:
  docx:
    reference-doc: caru-template.docx
    fig-width: 7
editor: visual
params: 
  com_name: "ballina"
title: '`r paste("Impact and Context Report: ", snakecase::to_title_case(params[["com_name"]]), " Centre of Mission")`'
execute: 
  echo: false
  warning: false
---

```{r libraries}
#| output: false
library(ggplot2)
library(knitr)
library(purrr)
library(here)
library(stringr)
library(dplyr)
library(snakecase)

com_name <- params[["com_name"]]

census_data <-
  readRDS(here("data", "census-data", 
               paste(com_name, "report-data.RDS", sep = "_")))

rtj_copy <- 
  readRDS(here("data", "rtj-report-copy",
               paste(com_name, "report-copy.RDS", sep = "_")))

desc_copy <- 
  readRDS(here("data", "com-descriptive-text",
               paste(com_name, "descriptive-copy.RDS", sep = "_")))

com_name <- to_title_case(com_name)

## There is no report copy for llanelli apparently

#TODO: Correct heading levels in rtj-data project
```

## Introduction

This short report provides an overview of the work that's been taking place at `r com_name` Centre of Mission (CoM) throughout the financial year 2022-2023, then situates that work within its local context using national census data.

The first section of this report summarises data provided by Church Army evangelists in order to describe the activities undertaken by the CoM, as well as the CoM's social impact and the ways in which people are exploring and developing faith through the work of the CoM.

The second section of the report uses data from the *Central Statistics Office's* 2022 census of the Republic of Ireland to describe the population who live within the area local to the CoM.

## Section 1: Activities and impact

```{r}
#| output: asis
tranches <- unlist(rtj_copy[["tranches"]])

tranche_dates <- 
  list(c("April 2023",     "August 2023"),
       c("September 2023", "December 2023"),
       c("January 2024",   "March 2024"))


# Check if tranches covered form a continuous sequence
sequence <- identical(min(tranches):max(tranches), tranches)

bullet_points <- function(x){
  str_c("* ", x) |> 
    str_c(collapse = "\n")
}

if(identical(tranches, 1:3)){
  
  text <- ""
  } else if(sequence){
    
    dates <- c(tranche_dates[[min(tranches)]][1],
               tranche_dates[[max(tranches)]][2])
  
    text <-
      "\n\nDue to the availability of data, the statistics and figures in this section of the report summarise the Centre of Mission's activity between" |> 
    str_c(dates[1], "and", dates[2], sep = " ")
} else {
  
  text <- 
    "\n\nDue to the availability of data, the statistics and figures in this section of the report describe the Centre of Mission's activity during the following time periods:"
  
  times <- map_chr(tranche_dates, str_c, collapse = " - ")
  times <- times[tranches]
  bullets <- bullet_points(times)
  
  text <- str_c(text, bulleted_list(), collapse = "\n\n")
}

cat(text)
```

```{r}
#| output: asis
cat(rtj_copy[["activities_section"]])
```

{{< pagebreak >}}

```{r}
#| output: asis
cat(rtj_copy[["faith_copy"]])
```

```{r}
#| output: asis
cat(rtj_copy[["food_prov_intro"]])
```

```{r food_prov_table}
#| output: true
safe_kable <- function(x, ...){
  if(length(x) > 1 & !all(is.na(unlist(x)))){
    names(x) <- c(...)
    kable(x)
  }
}

safe_kable(
  rtj_copy[["food_prov_table"]],
  c("Food provision", "No. boxes/parcels/meals", "Details")
  )
```

```{r}
#| output: asis
cat(rtj_copy[["ess_prov_intro"]])
```

```{r}
#| output: true
safe_kable(
  rtj_copy[["ess_prov_table"]],
  c("Provision", "No. Items/parcels", "Details"))
```

```{r}
#| output: asis
cat(rtj_copy[["volunteers_copy"]])
```

```{r}
#| output: true
safe_kable(rtj_copy[["backgrounds_table"]], c("Church background", "%"))
```

{{< pagebreak >}}

## Section 2: Local context

This section of the report describes, at a high level, the characteristics of the area in which the CoM operates. Since many Centres of Mission are set up via a partnership between Church Army and a host diocese, each CoM's area of operation is compared to the population profiles of the local diocese as well as the nation as a whole.

The tables and figures in this section describe the CoM's area of operation in terms of:

-   Age

-   Ethnicity

-   Religion

-   Self-reported general health

-   Household composition

All the data in this section of the report were collected in the *Central Statistics Office'*s 2022 census of the Republic of Ireland.

### Methodology

Researchers consulted the lead evangelist at each CoM in order to determine the specific geographical areas in which the CoM operates. These might include, for example, the specific estate on which a CoM runs its activities, or a particular area of housing inhabited by regular attendees of the CoM's activities. The population characteristics of these areas were approximated via a weighted summation of the populations of the small areas of statistical geography (i.e. output areas) that intersected the area described by the lead evangelist. The weights for this summation were the respective relative intersections of each small area with the area under consideration.

{{< pagebreak >}}

### Age

@fig-age and @tbl-age respectively show the ages of the population at the local, diocesan and national level.

```{r desc_copy_age}
#| output: asis
cat(desc_copy[["age"]])
```

```{r age_plot}
#| label: fig-age
#| fig-cap: Population ages in 10 year bands
census_data[["plots"]][["age_five_year"]]
```

```{r age_table}
#| label: tbl-age
#| tbl-cap: Population ages in 10 year bands
census_data[["tables"]][["age_five_year"]] |> 
  kable()
```

{{< pagebreak >}}

### Ethnicity

@fig-ethnicity and @tbl-ethnicity show, at a very high level, the self-reported ethnicity of the population across each geography.

```{r desc_copy_ethn}
#| output: asis
cat(desc_copy[["ethnicity"]])
```

```{r ethnicity_plot}
#| label: fig-ethnicity
#| fig-cap: Population ethnicities
census_data[["plots"]][["ethnicity"]]
```

```{r ethnicity_table}
#| label: tbl-ethnicity
#| tbl-cap: Population ethnicities
census_data[["tables"]][["ethnicity"]] |> 
  kable()
```

{{< pagebreak >}}

### Religion

@fig-religion and @tbl-religion show the religious beliefs of the population across each geography.

```{r desc_copy_rel}
#| output: asis
cat(desc_copy[["religion"]])
```

```{r religion_plot}
#| label: fig-religion
#| fig-cap: Population religions
census_data[["plots"]][["religion"]]
```

```{r religion_table}
#| label: tbl-religion
#| tbl-cap: Population religions
census_data[["tables"]][["religion"]] |> 
  kable()
```

{{< pagebreak >}}

### General health

@fig-general-health and @tbl-general-health show the self-reported general health of the population across each geography.

```{r desc_copy_general_health}
#| output: asis
cat(desc_copy[["general_health"]])
```

```{r general_health_plot}
#| label: fig-general-health
#| fig-cap: Population self-reported general health
census_data[["plots"]][["general_health"]]
```

```{r general_health_table}
#| label: tbl-general-health
#| tbl-cap: Population self-reported general health
census_data[["tables"]][["general_health"]] |> 
  kable()
```

{{< pagebreak >}}

### Household composition

@fig-household-composition and @tbl-household-composition give a summary of the prevalence of different kinds of household across all geographies.

```{r desc_copy_hh_overview}
#| output: asis
cat(desc_copy[["hh_overview"]])
```

```{r household_composition_plot}
#| label: fig-household-composition
#| fig-cap: Population household distribution overview
census_data[["plots"]][["household_grouped"]]
```

```{r household_composition_table}
#| label: tbl-household-composition
#| tbl-cap: Population household distribution overview
census_data[["tables"]][["household_composition"]] |> 
  kable()
```

{{< pagebreak >}}

## Local Deprivation

@fig-deprivation-map shows a map of relative deprivation of the local area. Small areas that are coloured in red are in the 5% most deprived areas nationally, those coloured orange are in the 10% most deprived, and those coloured yellow are in the 20% most deprived. Transparent areas are outside of the 20% most deprived areas in the nation.

Relative deprivation data is sourced from the 2017 Northern Ireland Multiple Deprivation Measures (NIMD). If you would like to know more about NIMD, you can find out about it [here](https://www.nisra.gov.uk/sites/nisra.gov.uk/files/publications/NIMDM17-%20with%20ns.pdf).

```{r imd_map}
#| output: asis
#| fig-width: 4
#| fig-cap: Map of local deprivation (IMD2019)

  cat(str_c("![fig-cap: Map of local deprivation (NIMD2017)]",
          "(imd-images/", params[["com_name"]], ".png)",
          "{#fig-deprivation-map fig-alt=\"A map of local deprivation levels\" " ,
          "width=70%}"))
```
